% Cover letter using letter.sty
\documentclass{letter} % Uses 10pt
%Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=8in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}

\signature{Ruban Palani}           % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
 
\begin{letter}{
Hiring Manager \\
Toronto Transit Commission \\
1900 Yonge St \\
Toronto, ON M4S 1Z2}


\begin{flushleft}
{\large\bf Ruban Palani}
\end{flushleft}
\medskip\hrule height 1pt
\begin{flushright}
\hfill 82 Adanac Dr, Toronto, ON M1M 2E4 \\
\hfill (647) 391-6666 
\end{flushright} 
\vfill % forces letterhead to top of page

 
\opening{Dear Hiring Manager:} 
 
\noindent I'm writing in regards to the Senior Systems Analyst opening posted on the TTC 
company site. With a bachelors degree in Computer Engineering and extensive hands-on 
experience using .Net languages to create and implement software applications. I am confident I will be an asset to your organization.
 
\noindent As a highly self-motivated and detailed oriented individual who thoroughly enjoys problem solving and teamwork. I believe I would be an excellent fit for this position. Throughout the years I've spent as a developer I gained valuable experience and excellent proficiency as a developer and engineer. Working in a firm such as yours will aid in reinforcing and building on this knowledge. Additionally, I am very comfortable 
applying knowledge in a rapid and time-constrained manner as is often the case in 
corporate environment.

\noindent My curiosity has always motivated me to develop a fundamental understanding of new topics and bridge gaps in my understanding as frequently as I can. I find it exciting and a crucial aspect to understand all aspects of a system to diagnose and debug a technical issue. I approach new challenges with confidence and excitement in what I can learn, which enables me to pick up and apply new technologies, programming languages and principles as needed. I highly value a friendly, collaborative environment where one can both help other team members and learn from them and this is one of my 
favourite aspects of a collaborative environment.
 
 
\noindent Becoming a part of the Toronto Transit Commision is just the kind of opportunity I am looking for to challenge myself and apply my skills towards something I’m very passionate about. It would give me great pleasure to have the opportunity to discuss future employment and to personally speak with you. If you have any questions or require any additional details please do not hesitate to contact me
 
\closing{Sincerely yours,} 
 

 
\encl{}  				% Enclosures

\end{letter}
 

\end{document}






